Linial-Mansour-Nisan Theorem

### 2020-11-12 CS590/paper.tex
Commiting finished presentation slides for circuit complexity class

\begin{corollary} \label{fouriertail}
  Let $f$ be a boolean function computred by a circuit of size $M$ and depth $d$. Then
  $$ Pr[\text{deg}(f_{\rho}) > s] \leq M2^{-s} $$
  where $\rho$ is a random restriction where $p = \frac{1}{10^ds^{d-1}}$
\end{corollary}
%
\begin{proof}
   First, we will repeatedly iterate the switching lemma to reduce the depth of $f$ through random restrictions such that the bottom fan-in at each step is at most $s$. This is accomplished by sampling the first round of restrictions $\rho_0$ to parameter $p_0 = \frac{1}{10}$ and by sampling the subsequent $d-1$ rounds $\rho_i$ according to parameter $p_i = \frac{1}{10s}$. We begin by claiming that, after the first restriction, the bottom gates' fan-ins are at most $s$. This can be decomposed into two cases:
   %
   \begin{enumerate}
     \item Suppose a gate initially has fan-in of at least $2s$ and (w.l.o.g) suppose that it is a $\wedge$-gate. The probability of $\rho_0$ setting at least of the input variables to $0$ is at most $(\frac{1}{10} + \frac{9}{20})^{2s} = (0.55)^{2s} < 2^{-s}$.
     \item Suppose a gate initially has fan-in of at most $2s$. The probability of $\rho$ setting at least $s$ of the input variables to $*$ is ${2s \choose s}(1/10)^s < 2^{-s}$
   \end{enumerate}
   %
  Since we assume that the $\AC^0$ circuit computing $f$ is in alternating normal form, once we invoke the switching lemma for the bottom two layer gates, we can merge the two $\vee$-gates to reduce the depth by one. The switching tells us that with probability of at least $1 - (5\frac{1}{10s}s)^s < 2^{-s}$, we can reduce the depth in each step such that the gates of distance two from the input variables have bottom fan-in of at most $s$. By the end of our depth-reduction routine, we are left with a CNF with bottom fan-in of at most $s$. Invoking Corollary (\ref{hastaddegree}) tells us that our final restricted function $f_{\rho_0\rho_1...\rho_{d-1}}$ has Fourier degree of at most $s$ with probability $< 2^{-s}$. The final bound arises from the observation that we applied the beginning analysis for each of the bottom gates exactly once, the switching lemma exactly once for each gate except for the output gate, and we invoked the corollary for the output gate. Each step contributed probability of $< 2^{-s}$.
\end{proof}
%
Corollary \ref{fouriertail} tells us that the probability of the Fourier degree exceeding $s$ decays exponentially with $s$ given that we set our probability parameter to a specific quantity $p = \frac{1}{10^ds^{d-1}}$.

@@

  \mathbb{E}_{x_V}||f^{>k}_{x_V}||_2^2 = \mathbb{E}_{x_V}\sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} |\widehat{f_{x_V}}(H)|^2 = \sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} \sum_{J \subseteq V} |\hat{f}(H \cup J)|^2 = \sum_{ \substack {S \subseteq [n] \\ |S \cap \overline{V}| > k}} |\hat{f}(S)|^2

>>>>

\begin{corollary} \label{fouriertail}
  Let $f$ be a boolean function computed by a circuit of size $M$ and depth $d$. Then
  $$ Pr[\text{deg}(f_{\rho}) > s] \leq M2^{-s} $$
  where $\rho$ is a random restriction where $p = \frac{1}{10^ds^{d-1}}$
\end{corollary}
%
\begin{proof}
   First, we will repeatedly iterate the switching lemma to reduce the depth of $f$ through random restrictions such that the bottom fan-in at each step is at most $s$. This is accomplished by sampling the first round of restrictions $\rho_0$ to parameter $p_0 = \frac{1}{10}$ and by sampling the subsequent $d-1$ rounds $\rho_i$ according to parameter $p_i = \frac{1}{10s}$. We begin by claiming that, after the first restriction, the bottom gates' fan-ins are at most $s$ with probability of at least $1 - 2^{-s}$. This can be decomposed into two cases:
   %
   \begin{enumerate}
     \item Suppose a gate initially has fan-in of at least $2s$ and (w.l.o.g) suppose that it is a $\wedge$-gate. The probability of $\rho_0$ setting at least of the input variables to $0$ is at most $(\frac{1}{10} + \frac{9}{20})^{2s} = (0.55)^{2s} < 2^{-s}$.
     \item Suppose a gate initially has fan-in of at most $2s$. The probability of $\rho$ setting at least $s$ of the input variables to $*$ is ${2s \choose s}(1/10)^s < 2^{-s}$
   \end{enumerate}
   %
  Since we assume that the $\AC^0$ circuit computing $f$ is in alternating normal form, once we invoke the switching lemma for the bottom two layer gates, we can merge the two $\vee$-gates to reduce the depth by one. The switching tells us that with probability of at least $1 - (5\frac{1}{10s}s)^s < 2^{-s}$, we can reduce the depth in each step such that the gates of distance two from the input variables have bottom fan-in of at most $s$. By the end of our depth-reduction routine, we are left with a CNF with bottom fan-in of at most $s$. Invoking Corollary (\ref{hastaddegree}) tells us that our final restricted function $f_{\rho_0\rho_1...\rho_{d-1}}$ has Fourier degree of at most $s$ with probability $< 2^{-s}$. The final bound arises from the observation that we applied the beginning analysis for each of the bottom gates exactly once, the switching lemma exactly once for each gate except for the output gate, and we invoked the corollary for the output gate. Each step contributed probability of $< 2^{-s}$.
\end{proof}
%
Corollary \ref{fouriertail} tells us that the probability of the Fourier degree exceeding $s$ decays exponentially with $s$ given that we set our probability parameter to a specific quantity $p = \frac{1}{10^ds^{d-1}}$.

@@

  \mathbb{E}_{x_V}||f^{>k}_{x_V}||_2^2 = \mathbb{E}_{x_V}\sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} |\widehat{f_{x_V}}(H)|^2
  & = \sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} \sum_{J \subseteq V} |\hat{f}(H \cup J)|^2 \\
  & = \sum_{ \substack {S \subseteq [n] \\ |S \cap \overline{V}| > k}} |\hat{f}(S)|^2

### 2020-11-12 CS590/slides.tex
Commiting finished presentation slides for circuit complexity class

\documentclass{beamer}
\usepackage{pgfpages}

@@

\section{Fourier Analysis on Boolean Functions}
\subsection{sub a}

\begin{frame}
\frametitle{List}
\begin{itemize}
\pause
\item Point A
\pause
\item Point B
\begin{itemize}
\pause
\item part 1
\pause
\item part 2
\end{itemize}
\pause
\item Point C
\pause
\item Point D
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{More Lists}
\begin{enumerate}[(I)]
\item<1-> Point A
\item<2-> Point B
\begin{itemize}
\item<3-> part 1
\item<4-> part 2
\end{itemize}
\item<5-> Point C
\item<-2,4-5,7> Point D
\end{enumerate}
\end{frame}

\subsection{sub b}
\setbeamercovered{transparent}
\begin{frame}
\frametitle{Overlays}
\only<1>{First Line of Text}

\only<2>{Second Line of Text}

\only<3>{Third Line of Text}
\end{frame}

\begin{frame}
\frametitle{Overlay Compatible Commands}
\textbf<2>{Example Text}

\textit<3>{Example Text}

\textsl<4>{Example Text}

\textrm<5>{Example Text}

\textsf<6>{Example Text}

\textcolor<7>{orange}{Example Text}

\alert<8>{Example Text}

\structure<9>{Example Text}
\end{frame}

\begin{frame}
\label{columns}
\frametitle{Using Columns}
\begin{columns}
\column{0.5\textwidth}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\column{0.5\textwidth}
\end{columns}
\end{frame}

\section{Section 2}

\begin{frame}
Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.
\end{frame}

\begin{frame}
\frametitle{Descriptions}
\begin{description}
\item[API] Application Programming Interface
\item[LAN] Local Area Network
\item[ASCII] American Standard Code for Information Interchange
\end{description}
\end{frame}

\begin{frame}
\frametitle{Blocks}
\begin{block}{Block Title}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
\end{block}
\begin{alertblock}{Block Title}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
\end{alertblock}
\end{frame}

\begin{frame}
\frametitle{More Blocks}
\begin{definition}
A prime number is a number that...
\end{definition}
\begin{example}
Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua.
\end{example}
\end{frame}

\begin{frame}
\frametitle{Maths Blocks}
\begin{theorem}<1->[Pythagoras]
$ a^2 + b^2 = c^2$
\end{theorem}
\begin{corollary}<3->
$ x + y = y + x  $
\end{corollary}
\begin{proof}<2->
$\omega +\phi = \epsilon $
\end{proof}
\end{frame}

\begin{frame}[fragile]
\frametitle{Including Code}
\begin{semiverbatim}
\\begin\{frame\}
\\frametitle\{Outline\}
\\tableofcontents
\\end\{frame\}
\end{semiverbatim}
\end{frame}

\begin{frame}
\frametitle{buttons}
\hyperlink{contents}{\beamerbutton{contents page}}

\hyperlink{columns}{\beamergotobutton{columns page}}

\hyperlink{pictures}{\beamerskipbutton{pictures page}}

\hyperlink{pictures}{\beamerreturnbutton{pictures page}}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage{pgfpages}
\usepackage{complexity}

@@

\section{Fourier Analysis on Boolean Functions}
\subsection{Characters}

\begin{frame}
\frametitle{Characters}
Let us first define some general concepts for any finite abelian group $G$.

\begin{enumerate}
\begin{definition}
  A group homomorphism from $\chi: G \rightarrow \mathbb{C}^*$ is called a \emph{character} of $G$ where $\mathbb{C}^* = \mathbb{C}/\{0\}$
\end{definition}

\item We call the homomorphism $\chi_0:G \rightarrow \mathbb{C}^*, \; \chi_0 = 1$ the \emph{trivial character} of $G$.
\item $\chi(a + b) = \chi(a)\chi(b)$
\item  The characters of $G$ form an abelian group $\hat{G}$ under pointwise multiplication of complex-valued functions. The group $\hat{G}$ is known as the \emph{character group} of $G$.
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Characters}
  \begin{enumerate}
    \item It follows from basic properties of cyclic groups that the only characters of $\mathbb{Z}_n$ are ones of the form $$ \chi_j(x) = e^{ 2\pi i jx/n} \quad j \in [n], \; x \in \mathbb{Z}_n $$ Note that each character is associated to an element of the group $j \in \mathbb{Z}_n$
    \begin{theorem}[Characters for finite abelian groups]
    For any finite abelian group $G \cong \mathbb{Z}_{n_1} \times \mathbb{Z}_{n_2} \cdots \times\mathbb{Z}_{n_k}$: the characters for $G$ will be:
    $$   \chi_a(x) = \prod_{i \in [k]} e^{2 \pi i a_k x_k/ n_k} $$
    for $a \in \mathbb{Z}_{n_1} \times \mathbb{Z}_{n_2} \cdots \times\mathbb{Z}_{n_k}$
    \end{theorem}
  \end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Characters}
  \begin{enumerate}
    \item It turns out the characters live in the vector space $L_2(G)$ i.e maps from $\phi: G \rightarrow \mathbb{C}$ square-integrable in respect to the uniform probability measure: $\frac{1}{|G|}\sum_{x \in G} |\phi(x)|^2 < \infty$
    \item Actually a Hilbert space endowed with the inner product:
    $$ \langle f,g \rangle = \frac{1}{|G|}\sum_{x\in G} f(x)\overline{g(x)}= \mathbb{E}_x f(x)\overline{g(x)} $$
    \begin{theorem}
      The characters $\chi \in \hat{G}$ form an orthonormal basis for $L_2(G)$
    \end{theorem}
    \item
    With any orthonormal basis, one can decompose any vector into its direct sum decomposition.
  \end{enumerate}
\end{frame}

\begin{frame}
\frametitle{Characters}
  \begin{enumerate}
    \item We restrict our attention to the finite abelian group $\mathbb{Z}_2^n$ as a natural group to define boolean functions $f: \{0,1\}^n \rightarrow \{0,1\}$.
    \item By the observations above, we conclude that our characters for $\mathbb{Z}_2^n = \mathbb{Z}_2 \times ... \times \mathbb{Z}_2$ are defined as
    $$  \chi_a(x) = (-1)^{\sum_{i \in [n]} x_ia_i} = (-1)^{\sum_{i \in [n], \; a_i = 1} x_i}$$
    where $x_i$ is the $i^{th}$ bit of $x \in \{0,1\}^n$.
    \begin{block}{Some Notation}
      Let $S \subseteq [n]$ be such that $S_x = \{i \mid x_i = 1\}$. As there is a bijective correspondence between all such subsets $S_x$ and $x \in \{0,1\}^n$, we will sometimes identify bit strings with their subset counterparts
      $$ \chi_A(x) = (-1)^{\sum_{i \in A} x_i}, \quad A \subseteq [n]$$
    \end{block}
  \end{enumerate}
\end{frame}

\subsection{The Fourier Transform}
\begin{frame}
\frametitle{The Fourier Transform}
  \begin{enumerate}
    \item Given any $f \in L_2(G)$, let $\hat{f}: \hat{G} \rightarrow \mathbb{C}$ be the complex-valued function such that
    $$  \hat{f}(\chi_a) =  \langle f, \chi_a \rangle, \; a \in G $$
    These are the projections onto the orthonormal basis of characters. We deem $\hat{f}$ the \emph{Fourier Transform} of $f$.
    \item The direct sum decomposition of $f$ yields the following form known as the \emph{Fourier Inversion Formula}:
    $$  f = \sum_{a \in G} \hat{f}(\chi_a)\chi_a $$
    The complex value $\hat{f}(\chi_a)$ is called the \emph{Fourier coefficient} associated to $\chi_a$
    \item From the above definition, we directly calculate that
    $$  \hat{f}(0) = \langle f, \chi_0 \rangle = \mathbb{E}_x f(x) $$
  \end{enumerate}
\end{frame}

\begin{frame}
\frametitle{The Fourier Transform}
\begin{enumerate}
  \item
  Let $f = \text{Maj}_3$ where $G = \mathbb{Z}_2^n$.
  \begin{align}
    & \hat{f}(0^3) = \mathbb{E}_x[f(x)] = \frac{1}{2} \\
    & \hat{f}(\{001,010,100\}) = - \frac{1}{4} \\
    & \hat{f}(\{011,110,101\}) = 0 \\
    & \hat{f}(1^3) = \frac{1}{8}\sum_{x \in \{0,1\}^3} (-1)^{|x|}f(x) = \frac{1}{4}
  \end{align}
  \begin{definition}
    Let $f:\{0,1\}^n \rightarrow \{0,1\}$ be an $n$-ary boolean function. The \emph{Fourier degree} of $f$, denoted by def$_{\mathcal{F}}(f)$, is the largest $|S|$ such that $\hat{f}(S) \neq 0$.
  \end{definition}
  For the case of f = Maj$_3$, def$_{\mathcal{F}}(f) = 3$
\end{enumerate}
\end{frame}

\begin{frame}
\frametitle{The Fourier Transform}
  \begin{theorem}[Parseval's Identity]
    Let $f \in L_2(G)$. Then
    $$ ||f||_2^2 = \sum_{a \in G} |\hat{f}(a)|^2$$
  \end{theorem}
  \begin{proof}
    \begin{align*}
      ||f||^2_2 = \langle f, f \rangle = \langle \sum_{a \in G} \hat{f}(a) \chi_a,  \sum_{b \in G} \hat{f}(b) \chi_b \rangle & = \sum_{a,b \in G} \hat{f}(a)\overline{\hat{f}(b)}\langle \chi_a, \chi_b \rangle \\
      & = \sum_{a \in G} |\hat{f}(a)|^2
    \end{align*}

    The last equality is just the orthonormality of the characters.
  \end{proof}
\end{frame}

\section{LMN Theorem}

\begin{frame}
  \frametitle{LMN Theorem}
  \begin{theorem} (Linial, Mansour, Nisan) \label{lmn}
      Let $f$ be a boolean fucntion computed by a circuit of depth $d$ and size $M$ and let $t$ be any non-negative integer. Then
      \begin{equation}
        \sum_{|S| > t} |\hat{f}(S)|^2 \leq 2M2^{-t^{1/d}/20}
      \end{equation}
  \end{theorem}
  The theorem reveals that the $t$-tails of the Fourier spectrum, i.e strings indexed by sets $|S| > t$, become exponentially small in $t$ for boolean functions in $\AC^0$.
\end{frame}

\begin{frame}
  \frametitle{LMN Theorem}

  \begin{theorem}[\emph{H\aa stad}]
    Let $f$ be given by a CNF-formula where each clause has size at most $t$, and choose a random restriction $\rho$ with parameter $p$ such that $Pr[\rho(x_i)] = p$ for all input variables $x_i$. With probability of at least $1 - (5pt)^s$, $f_{\rho}$ can be expressed as a DNF formula where each clause has size of at most $s$, and the clause all accept disjoint sets of inputs i.e no string $x \in \{0,1\}^n$ satisfies more than one clause.
  \end{theorem}

  \begin{corollary} \label{hastaddegree}
  Let $f$ be a boolean function computed by a CNF of bottom fan-in of at most $t$, and $\rho$ is a $p$-random restriction, then
  \begin{equation}
    Pr[\text{deg}_{\mathcal{F}}(f_\rho) > s] < (5pt)^s
  \end{equation}
  \end{corollary}

\end{frame}

\begin{frame}
  \frametitle{LMN Theorem}
  \begin{corollary}[Tail Degree Corollary] \label{fouriertail}
    Let $f$ be a boolean function computed by a circuit of size $M$ and depth $d$. Then
    $$ Pr[\text{deg}(f_{\rho}) > s] \leq M2^{-s} $$
    where $\rho$ is a random restriction where $p = \frac{1}{10^ds^{d-1}}$
  \end{corollary}
  \pause
  \begin{proof}[Proof Sketch]
    Show that first random restriction of parameter $p_0 = \frac{1}{10}$, the bottom gates' fan-ins are at most $s$ with probability of at least $1 - 2^{-s}$. Then iterate H\aa stad's switching lemma with under $p_i = \frac{1}{10s}$ on each gate of distance two fromm the input variables to turn them into DNFs with disjoint inputs. Collapse a level and the lemma ensures that the new bottom fan-in is at most $s$. Stop when we are left with a CNF (depth-2) with bottom fan-in of at most $s$ and invoke the previous corollary.
  \end{proof}
\end{frame}

\begin{frame}
  \frametitle{Proof of LMN Theorem}
  \begin{definition}
    Let $k$ be a positive integer and $f:\mathbb{Z}_2^n \rightarrow \mathbb{C}$ a complex-valued function on $\mathbb{Z}_2^n$. We define: \newline
    $$f^{\leq k} := \sum_{|S| \leq k} \hat{f}(S)\chi_{S} $$
    The notation symbols $f^{=k},f^{\geq k}$ are defined in the same manner.
  \end{definition}
  \pause
  \begin{enumerate}
    \item We begin by first setting our probability parameter $p \leq \frac{1}{10^dk^{d-1}}$. The values $p, k$ will be fixed later to invoke the Tail Degree Corollary above.
    \pause
    \item
    Recall how we sample a random restriction $\rho$ by sampling some $V \subseteq [n]$ to be the indices which are \emph{not} set to $*$. Each index has a $1-p$ probability of being set to either $0,1$. For each index in $V$, we uniformly sample some bit string in $\{0,1\}^{|V|}$ to fix the indices contained in $V$.
    \pause
    \item Let $x_{V}$ be the restriction of string $x$ on the input indices to those found in $V$
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Proof of LMN Theorem}
  \begin{enumerate}
    \item If we recall that our characters are defined as $\chi_A(x) = (-1)^{\sum_{i \in A} x_i}$
    \pause
    \begin{block}{How characters separate}
      \begin{align*}
        \chi_S(x) = (-1)^{\sum_{i \in S} x_i}
        & = (-1)^{\sum_{i \in S \cap V} x_i + \sum_{i \in S / V} x_i}   \\
        & = (-1)^{\sum_{i \in S \cap V} x_i}(-1)^{\sum_{i \in S / V} x_i} = \chi_{S \cap V}(x_V) \chi_{S / V}(x_{\overline{V}})
      \end{align*}
    \end{block}
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Proof of LMN Theorem}
  \begin{enumerate}
    \item If we set $x_V$ to some bit string, it makes sense to think of $f_{x_V} = f(x_V,*)$ as a function $f_{x_V}: \{0,1\}^{|x_{\overline{V}}|} \rightarrow \{0,1\}$.
    \pause
    \item By our Fourier Inversion Formula and the observation in the previous slide:
    \begin{align*}
    f(x)
    & = \sum_{S \subseteq [n]} \hat{f}(S)\chi_{S}(x) =  \sum_{V \sqcup \overline{V} \subseteq [n]} \hat{f}(S)\chi_{S \cap V}(x_V)\chi_{S / V}({x_{\overline{V}}}) \\
    & = \sum_{H \subseteq \overline{V}} \left( \sum_{J \subseteq V} \hat{f}(H \cup J) \chi_{J}(x_V) \right) \chi_H(x_{\overline{V}})
  \end{align*}
    \item
    Since the Fourier decomposition is unique for $f_{x_V}$,
    \begin{equation*}
      \widehat{f_{x_V}}(H) = \sum_{J \subseteq V} \hat{f}(H \cup J)\chi_{J}(x_V), \quad H \subseteq \overline{V}
    \end{equation*}
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Proof of LMN Theorem}
  \begin{enumerate}
    \item By Parseval's identity on the function $x_T \mapsto \widehat{f_{x_T}}(H)$,
    \begin{equation}
      \mathbb{E}_{x_V}|\widehat{f_{x_V}}(H)|^2 = \langle \hat{f}_{-}(H), \hat{f}_{-}(H) \rangle = \sum_{J \subseteq V} |\hat{f}(H \cup J)|^2
    \end{equation}
    \pause
    \item
    This along with another application of Parseval's identity yields the string of equalities: \newline
    \begin{align}
      \mathbb{E}_{x_V}||f^{>k}_{x_V}||_2^2 = \mathbb{E}_{x_V}\sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} |\widehat{f_{x_V}}(H)|^2
       & = \sum_{\substack {H \subseteq \overline{V} \\ |H| > k}} \sum_{J \subseteq V} |\hat{f}(H \cup J)|^2 \\
       & = \sum_{ \substack {S \subseteq [n] \\ |S \cap \overline{V}| > k}} |\hat{f}(S)|^2
    \end{align}
  \end{enumerate}
\end{frame}

\begin{frame}
  \frametitle{Proof of LMN Theorem}
  \begin{enumerate}
    \item Sampling over all such $p$-restrictions further shows that the lefthand side is upper bounded by:
    \begin{equation*} \label{coroinvoke}
      \mathbb{E}_V\mathbb{E}_{x_V} ||f^{>k}_{x_V}||_2^2 = \mathbb{E}_{\rho} ||f^{>k}_{\rho}||_2^2 \leq Pr[\text{deg}_{\mathcal{F}}(f_\rho) > k] \leq M2^{-k}
    \end{equation*}
    \pause
    \item A Chernoff bound argument shows that the righthand side is lower bounded by:
    $$ \sum_{|S| > t} |\hat{f}(S)|^2 \leq 2 \mathbb{E}_T \sum_{ \substack {S \subseteq [n] \\ |S \cap \overline{V}| > k}} |\hat{f}(S)|^2 $$
    for $k = pt/2$
    \pause
    \item Setting our constants $p = \frac{1}{10t^{(d-1)/d}}$ and $k = t^{1/d}/20$ shows that $p \leq \frac{1}{10^dk^{d-1}}$. This allows us to invoke our Tail Degree Corollary which gives us the desired inequality
    \begin{equation}
      \sum_{|S| > t} |\hat{f}(S)|^2 \leq 2M2^{-t^{1/d}/20}
    \end{equation}
  \end{enumerate}
\end{frame}

\section{Consequences}
\subsection{Approximation by Low-degree Polynomials}

\begin{frame}
  \frametitle{Approximation by Low-degree Polynomials}
   Theorem (\ref{lmn}) shows that we can approximate functions in $f \in \AC^0$ by taking our polynomials to be $f^{\leq k}$ for some sufficiently large $k$. Here we make the distinction that our Fourier expansion of $f$ will be
  $$f = \sum_{S \subseteq [n]} \hat{f}(S) \prod_{i \in S} x_i $$ as a polynomial with complex coefficients.
  \begin{lemma}
    Let $f \in \AC^0$ be a boolean function of polynomial size and depth $d$. Then there exists a complex polynomial of degree $\mathcal{O}((\log{n/\epsilon})^d)$ such that $||f - p ||_2 < \epsilon$
  \end{lemma}
\end{frame}

\subsection{Sensitivity and Influence}

\begin{frame}
  \frametitle{Sensitivity and Influence}
  LMN also shows that functions in $\AC^0$ have low average sensitivity i.e its output is not very sensitive to changes to the input.
  \begin{definition}
    Let $f: \{0,1\}^n \rightarrow \{0,1\}$ be a boolean function. We define the \emph{sensitivity} of an input $x\in \{0,1\}^n$ in respect to $f$, $s_f(x)$ to be the number of indices $i$ such that $f(x) \neq f(x + e_i)$ where $e_i$ is the bit string with zeros everywhere except for the $i^{th}$ index.
  \end{definition}

  \begin{definition}
    Let $f: \{0,1\}^n \rightarrow \{0,1\}$ be a boolean function. The \emph{influence} of $f$, $I_f$ is defined as the average sensitivity over all input bit strings
    \begin{equation}
      I_f = \mathbb{E}_x[s_f(x)]
    \end{equation}
  \end{definition}
\end{frame}

\begin{frame}
  \frametitle{Sensitivity and Influence}
  The influence of $f$ can be expressed in terms of its Fourier coefficients:

  \begin{equation}
    I_f = 4\sum_{S \subseteq [n]} |S||\hat{f}(s)|^2
  \end{equation}

  By combining this equivalence with Theorem (\ref{lmn}), we deduce the following upper bound on the influence of a function in $\AC^0$

  \begin{lemma} \label{influence}
    Let $f \in \AC^0$ be of depth $d$. Then
    \begin{equation}
      I_f = \mathcal{O}((\log n)^d)
    \end{equation}
  \end{lemma}
  The lemma shows that functions in $\AC^0$  are not suitable for constructing universal hash functions and pseudorandom function generators.
\end{frame}

\begin{frame}
  \frametitle{Sensitivity and Influence}
  \begin{definition}
    A function $f:\{0,1\}^m \times \{0,1\}^n \rightarrow \{0,1\}$ is called a \emph{pseudorandom function generator} if there exists no polynomial-time oracle Turing machine which can distinguish between the outputs from a true random oracle versus $f(s,_)$ for some random seed $s \in \{0,1\}^m$.
  \end{definition}

  \begin{lemma}
    No pseudorandom function generators exist in $\AC^0$
  \end{lemma}
  By taking advantage of the low average sensitivity, we can simply perturb the input slightly and check if the output of $f$ changes. If it doesn't, there is a good chance that
  it lies in $\AC^0$.
\end{frame}
